Sustainable computational science:\\ the ReScience initiative

### 2017-07-13 draft.tex
make wording more formal #40

\textbf{(\cite{stachelek:2016})} I was motivated to replicate the results of
the original paper because I feel that working through code supplements to blog
posts has really helped me learn how to science. I could have published my
replication as a blog post but I wanted the exposure and permanency that goes
along with journal articles. This was my first experience with formal
replication. I think the review was useful because it forced me to consider how
the replication would be used by people other than myself. I have not yet
experienced any new interactions following publication. However, I did notify
the author of the original implementation about the replication's
publication. I think this may lead to future correspondence. The original
author suggested that he would consider submitting his own replications to
ReScience in the future.\\

>>>>

\textbf{(\cite{stachelek:2016})} I was motivated to replicate the results of
the original paper because I feel that working through code supplements to blog
posts has really helped me learn the process of scientific analysis. I could 
have published my replication as a blog post but I wanted the exposure and 
permanency that goes along with journal articles. This was my first experience 
with formal replication. I think the review was useful because it forced me to 
consider how the replication would be used by people other than myself. I have 
not yet experienced any new interactions following publication. However, I did 
notify the author of the original implementation about the replication's 
publication. I think this may lead to future correspondence. The original author suggested that he would consider submitting his own replications to
ReScience in the future.\\
